\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{amsmath, amsthm, amssymb, appendix, bm, graphicx, hyperref, mathrsfs, tabularx}
\usepackage{mdframed}
\usepackage{subcaption, float}
\usepackage{caption}
\newcommand{\ZW}[1]{\textcolor{magenta}{$\mathcal{ZW}$:~#1}}
\newcommand{\ZZH}[1]{\textcolor{orange}{$\mathcal{ZZH}$:~#1}}

\definecolor{commentgray}{rgb}{0.95,0.95,0.95}
\definecolor{revcolor}{rgb}{0.0, 0, 255} 
\definecolor{oldcolor}{rgb}{0.8, 0.0, 0.0}

\newenvironment{reviewercomment}[1]{
    \vspace{1em}
    \noindent \textbf{#1:} \itshape
}{
    \par\vspace{0.5em}
}

\newenvironment{authorresponse}{
    \noindent \textbf{Reply:} \normalfont
}{
    \par\vspace{1.5em}
}

\newenvironment{originaltext}{
    \begin{quote}
    \color{oldcolor} \small \textbf{Original text:} \\
}{
    \end{quote}
}

\newenvironment{revisedtext}{
    \begin{quote}
    \color{revcolor} \small \textbf{Revised text:} \\
}{
    \end{quote}
}

\title{Replies to Editor Report}
\author{Manuscript ID: JCAP\_160P\_1025}
\date{}

\begin{document}

\noindent\rule{\textwidth}{0.8pt}

\begin{center}
{\LARGE\bfseries Replies to Editor Report\par}
\vspace{0.2cm}
{Manuscript ID: JCAP\_160P\_1025\par}
\end{center}
\vspace{-0.2cm}
\noindent\rule{\textwidth}{0.8pt}

\vspace{0.2cm}
\noindent Dear Editor and Reviewers,\\

We are grateful for the positive feedback and helpful suggestions from the reviewers.
We have revised our manuscript accordingly to ensure that the additional discussions are clear to the readers.
For clarity, the {\color{revcolor} revised content} in {\color{revcolor} blue}. 

\noindent\rule{\textwidth}{0.8pt}

I thank the authors for going carefully through the comments, and providing
point-by-point responses to them. \\

Regarding their responses to points 1 and 5, can the authors add these
plots as part of an appendix to the paper? This should clarify some points
that could also be raised by the readers. Otherwise, I would recommend
acceptance of this paper for publication.

\vspace{0.3cm}

\begin{authorresponse}
We thank the referee for helpful suggestions. We have added the relevant discussions and plots in the appendices of the revised manuscript.
Responses to point 1 are summarized in appendix~A while responses to point 5 are summarized in appendix~B.
Accordingly, we have also updated the main text to refer to these appendices for more details.

At page 7, we have added the following sentences to refer to the discussion in appendix~A:
\end{authorresponse}

\begin{revisedtext}
    Despite this, such a selection of events can still introduce biases in the inference of the Love-Q relation, 
    and we make a discussion on this issue in appendix~A.
\end{revisedtext}

    At page 8, we have added the following sentences to refer to the discussion in appendix~B:

\begin{revisedtext}
    Given that the Love-Q relation is quasi-universal with relative differences of $\sim 1\%$ for various EOSs, 
    the fitting uncertainties of the hyperparameters are also considered in the reference values. 
    To check the robustness of our conclusions, we repeat the inference assuming the SLy EOS; 
    these results are summarized in appendix~B.
\end{revisedtext}

\end{document}